\documentclass[version=last, paper=A4, DIV=12, toc=bibliography]{scrartcl}%
\directlua{pdf.setminorversion(7)}% chktex 36

%
% Packages
%

% Fonts, languages, and miscellaneous text commands
\usepackage{fontspec}%
\usepackage{fontawesome5}%
\usepackage[american]{babel}%
\usepackage{varwidth}%
\usepackage{relsize}%

% KOMA-Script
\usepackage{scrdate}%
\usepackage{scrlayer-scrpage}%

% Patching
\usepackage{xpatch}%

% Mathematics
\usepackage{mathtools}%
\usepackage{amsthm}%
\usepackage[ruled, longend]{algorithm2e}%
\usepackage{prftree}%
\usepackage[warnings-off={mathtools-colon,
  mathtools-overbracket}]{unicode-math}%

% Verbatim, colored boxes, and source code listings
\usepackage{fancyvrb}%
\usepackage{tcolorbox}%
\usepackage[newfloat]{minted}
\tcbuselibrary{many, minted}

% Microtypography and quotations
\usepackage[final, babel]{microtype}%
\usepackage[autostyle, autopunct, strict]{csquotes}%

% Numbers and units
\usepackage{siunitx}%
\usepackage{nth}%

% Tabulars, arrays, and lists
\usepackage{array}%
\usepackage[inline]{enumitem}%
\usepackage{booktabs}%

% Infix arithmetic
\usepackage{calc}%

% Links and references
\usepackage{hyperref}%
\usepackage{cleveref}%

% Bibliography
\usepackage[hyperref, block=space, sorting=ydnt, backend=biber]{biblatex}%

% Logos
\usepackage{hologo}%
\newcommand*{\CC}{%
  C\nolinebreak%
  \hspace{-.05em}\raisebox{.3ex}{\relsize{-2}{+}}\nolinebreak%
  \hspace{-.10em}\raisebox{.3ex}{\relsize{-2}{+}}%
}%

% Hyphens and dashes
\usepackage[shortcuts]{extdash}%

%
% Setup
%

\setromanfont{Libertinus Serif}
\setsansfont{Libertinus Sans}
\setmathfont{Libertinus Math}
\setmonofont[Scale=MatchLowercase]{Iosevka Term Slab}

\RedeclareSectionCommand[beforeskip=-.25\baselineskip]{section}%

\makeatletter%
\renewcommand*{\sectionlinesformat}[4]{%
  \ifstr{#1}{section}{%
    \parbox[t]{\linewidth}{%
      \raggedsection\@hangfrom{\hskip #2#3}{#4}\par%
      \kern-.75\ht\strutbox\rule{\linewidth}{.8pt}%
    }%
  }{%
    \@hangfrom{\hskip #2#3}{#4}%
  }%
}%
\makeatother%

\addbibresource{Publications.bib}%
\nocite{*}%
\AtBeginBibliography{\small}%

\newbibmacro*{name:bold}[2]{%
  \def\do##1{\iffieldequalstr{hash}{##1}{\bfseries\listbreak}{}}%
  \dolistloop{\boldnames}%
}%

\newcommand*{\boldnames}{}%

\xpretobibmacro{name:family}{%
  \begingroup\usebibmacro{name:bold}{#1}{#2}%
}{}{}%
\xpretobibmacro{name:given-family}{%
  \begingroup\usebibmacro{name:bold}{#1}{#2}%
}{}{}%
\xpretobibmacro{name:family-given}{%
  \begingroup\usebibmacro{name:bold}{#1}{#2}%
}{}{}%
\xpretobibmacro{name:delim}{%
  \begingroup\normalfont%
}{}{}%

\xapptobibmacro{name:family}{\endgroup}{}{}%
\xapptobibmacro{name:given-family}{\endgroup}{}{}%
\xapptobibmacro{name:family-given}{\endgroup}{}{}%
\xapptobibmacro{name:delim}{\endgroup}{}{}%

\renewcommand*{\boldnames}{}%
\forcsvlist{\listadd\boldnames}{%
  {90e97b67720ed4a478d19395e2c396d7}%
}%

\unimathsetup{%
  math-style=ISO, bold-style=ISO%
}%

\mathtoolsset{mathic}%

\sisetup{%
  detect-all, detect-display-math, binary-units%
}%

\hypersetup{%
  unicode,%
  breaklinks,%
  colorlinks,%
  pdftitle={Curriculum vitae -- Dario Gjorgjevski},% chktex 8
  pdfauthor={Dario Gjorgjevski},%
  pdfsubject={Curriculum vitae}%
}%

%
% Commands
%

\NewDocumentCommand{\Institution}{m}{\textsf{#1}}%
\NewDocumentCommand{\Unit}{m}{\textit{#1}}
\NewDocumentCommand{\ISODate}{m}{\texttt{#1}}%
\NewDocumentCommand{\Rounded}{o m}{%
  \num[round-mode=places, round-precision=\IfNoValueTF{#1}{2}{#1},
  round-integer-to-decimal]{#2}%
}%

\rofoot{(Typeset on \ISODate{\ISOToday})}%
\pagestyle{scrheadings}%

\NewDocumentCommand{\EducationEntry}{m m m m m m m m m}{%
  \noindent%
  \begin{tabular}{%
    p{.7\textwidth-2\tabcolsep}%
    >{\raggedleft\arraybackslash}p{.3\textwidth-2\tabcolsep}%
    }%
    \Institution{#2}                              & \ISODate{#1} \\
    \Unit{#3}                                     & #4           \\
    #5                                            & #6           \\
    GPA of \Rounded{#7}, scale #8                 &              \\
    \multicolumn{2}{p{\textwidth-2\tabcolsep}}%
    {%
    \begin{addmargin}{2em}
      \small#9\par%
    \end{addmargin}%
    }%
  \end{tabular}%
  \par%
}

% {Date}{Institution}[Unit]{Location}{Position}[Supervisors]{Description}
\NewDocumentCommand{\WorkEntry}{m m o m m o m}{%
  \noindent%
  \begin{tabular}%
    {%
    p{.7\textwidth-2\tabcolsep}%
    >{\raggedleft\arraybackslash}p{.3\textwidth-2\tabcolsep}%
    }
    \Institution{#2}          & \ISODate{#1} \\
    \IfNoValueTF{#3}{%
    #5                        & #4           \\
    }{%
    \Unit{#3}                 & #4           \\
    #5                        &              \\
    }
    \IfNoValueF{#6}{%
    Supervisors: #6           &              \\
    }
    \multicolumn{2}{p{\textwidth-2\tabcolsep}}%
    {%
    \begin{addmargin}{2em}
      \small#7\par
    \end{addmargin}%
    }
  \end{tabular}%
  \par%
}

%
% Document
%

\begin{document}

\begin{addmargin}{.2\textwidth}
  \begin{center}
    \LARGE\bfseries Dario Gjorgjevski
  \end{center}
  \begin{flushleft}
    \begin{description}[noitemsep, leftmargin=*]
    \item[\faHome] Kruševska \textnumero~21\hfill\textbullet\hfill 2320
      Delčevo\hfill\textbullet\hfill Macedonia
    \item[\faAddressCard] \href{mailto:dario.gjorgjevski@gmail.com}%
      {\nolinkurl{dario.gjorgjevski@gmail.com}}\hfill (+389)~72~215~992
    \end{description}
  \end{flushleft}
\end{addmargin}

\addsec{Education}\label{sec:education}

\EducationEntry%
{2013-09-15/2018-01-30}% chktex 8
{\href{http://ukim.edu.mk/}{Ss.\ Cyril and Methodius University}}%
{\href{https://finki.ukim.mk/}{Faculty of Computer Science and Engineering}}%
{Skopje, Macedonia}%
{Computer Science and Engineering}{Bachelor's degree}%
{10}{from 5 (E/F) to 10 (A)}%
{%
  Strong background in linear algebra, statistics, stochastic processes,
  compilers, machine learning, and cryptography.  Bachelor's thesis on
  code\-/based cryptography, titled \textquote{Error\-/Correcting Codes in the
    Rank Metric (With Applications to Cryptography)} and supervised by prof.\
  Simona Samardjiska.%
}

\begin{tcolorbox}[size=fbox, fontupper=\small, fontlower=\footnotesize]
  Over \num{40} \emph{Massive Open Online Courses} on topics related to game
  theory, probabilistic graphical models, Bayesian statistics, combinatorics,
  programming language theory, mathematical optimization, etc.%
  \tcblower%
  Certifications available at
  \url{https://github.com/d125q/Personal/tree/master/Certifications}.
\end{tcolorbox}

\addsec{Experience}\label{sec:experience}

\WorkEntry%
{2018-07-18/}% chktex 8
{\href{https://www.so1.ai/en/}{Segment of One}}%
{Berlin, Germany}%
{Data Engineering}%
{%
  \begin{itemize}[noitemsep, leftmargin=*]
  \item Modeling clients' business rules as \emph{minimum\-/cost flow} problems.
  \item Developing internal ETL tools and processes; implementing
    \emph{change data capture} for heterogeneous data sources.
  \item Configuring, monitoring, and optimizing Vertica clusters and databases.
  \end{itemize}
}

\WorkEntry%
{2017-11-20/2018-06-15}% chktex 8
{\href{http://infiniteanalytics.com/}{Infinite Analytics, Inc.}}%
{Skopje, Macedonia}%
{Data Science/Engineering}%
{%
  \begin{itemize}[noitemsep, leftmargin=*]
  \item Scraping of clients' websites and product catalogs using Scala/Akka and
    Python/Scrapy.
  \item Dynamic configuration of upstreams with persistence across restarts in
    NGINX Plus.
  \item Acquisition, monitoring, analysis, and visualization of server
    utilization data.
  \item Behavior\-/driven development of a Scala/Apache Spark program to compute
    and visualize \emph{customer insights} using over \num{2} billion facts
    about \num{50} million customers.
  \end{itemize}%
}

\WorkEntry%
{2017-07-07/09-20}% chktex 8
{\href{https://epfl.ch/}{École polytechnique fédérale de Lausanne}}%
[\href{http://lca.epfl.ch/}{Laboratory for Communications and Applications}]%
{Lausanne, Switzerland}%
{Research Internship}%
[%
\href{https://people.epfl.ch/276750}{Jagdish Prasad Achara} and
\href{https://people.epfl.ch/jean-yves.leboudec}{prof.\ Jean\=/Yves Le Boudec}%
]%
{%
  \begin{itemize}[noitemsep, leftmargin=*]
  \item Implementing software agents (\mintinline{python}{asyncio}) and network
    emulation (Mininet) in T\=/RECS, a \emph{Software \underline{T}estbed for
      Multi\-/Agent \underline{R}eal\-/Time Control of El\underline{ec}tric
      \underline{S}ystems}.
  \item Time series modeling of smart grid power traces at a timescale of
    \SI{20}{\ms} using approaches based on wavelets and long\-/range dependence.
  \item Increasing the resolution of mean\-/aggregated data using deep learning
    for super\-/resolution.
  \end{itemize}%
}

\WorkEntry%
{2016-10/2017-02}% chktex 8
{\href{http://ukim.edu.mk/}{Ss.\ Cyril and Methodius University}}%
[\href{https://finki.ukim.mk/}{Faculty of Computer Science and Engineering}]%
{Skopje, Macedonia}%
{Computer Laboratory Assistantship}%
{%
  Full responsibility for conducting computational exercises and homework
  assignments in:
  \begin{labeling}{Probability and Statistics}
  \item[Linear Algebra] Least squares, linear codes, and low\-/rank
    approximations with Mathematica and \textsc{SageMath}.
  \item[Probability and Statistics] Data visualization, Monte Carlo methods,
    statistical inference, hypothesis testing, and linear regression with R.
  \item[Databases] ER modeling, relational algebra, and ANSI SQL\@.
  \end{labeling}%
}

\WorkEntry%
{2016-06-15/09-15}%chktex 8
{\href{https://epfl.ch/}{École polytechnique fédérale de Lausanne}}%
[\href{https://lasec.epfl.ch/}{Security and Cryptography Laboratory}]%
{Lausanne, Switzerland}%
{Research Internship}%
[%
\href{https://lasec.epfl.ch/~bogos/}{Sonia Bogos} and
\href{https://lasec.epfl.ch/~vaudenay/}{prof.\ Serge Vaudenay}%
]%
{%
  Studying and improving upon the complexity of state\-/of\-/the\-/art solving
  algorithms for the \emph{Learning With Errors} (LWE) problem.%
}

\addsec{Honors and Achievements}\label{sec:honors-achievements}

\begin{itemize}
\item Best student paper at the \nth{14} International Conference on Informatics
  and Information Technologies held on April 7\==9, 2017 in Hotel Bistra,
  Mavrovo, Macedonia.
\item Scholarships to attend the
  \href{http://summerschool-croatia.cs.ru.nl/2016/}{2016} and
  \href{http://summerschool-croatia.cs.ru.nl/2017/}{2017} editions of the Summer
  School on Real\-/World Crypto and Privacy held in Šibenik, Croatia.
\item Dean's list at the Faculty for Computer Science and Engineering.
\item Merit\-/based scholarships from the Faculty of Computer Science and
  Engineering, the Ministry of Education and Science of Macedonia, and the
  Municipality of Delčevo.
\end{itemize}

\addsec{Skills}\label{sec:skills}

\subsection*{Programming and
  Computation}\label{subsec:programming-computation}

\begingroup
\setkomafont{labelinglabel}{\itshape}%
\begin{labeling}[~\==]{Academic exposure to}
\item[Proficient with]
  \begingroup
  \setkomafont{labelinglabel}{\normalfont}
  \begin{labeling}[~\==]{Python}
  \item[Python] NumPy, SciPy, Pandas, scikit\=/learn, Keras, Scrapy, NetworkX.
  \item[R] tidyverse, mlr, caret, interfaces to JAGS/Stan.

    Packages for time series analysis, network analysis, text mining.
  \item[SQL] Vertica, PostgreSQL, Redshift.
  \item[Shell] sh, Bash, Zsh.
  \item[CAS] Mathematica, \textsc{SageMath}.
  \item[(D)VCS] Git.%chktex 36
  \end{labeling}
  \endgroup
\item[Familiar with] Scala, C, C++, Java.
\item[Academic exposure to] various Lisps, Haskell, Standard ML\@.
\end{labeling}
\endgroup

\subsection*{Document Preparation}\label{subsec:document-preparation}

\begin{itemize}[leftmargin=*]
\item \Hologo{(La)TeX}, Jupyter, Sweave/knitr, Wolfram Notebooks.%chktex 36
\item Matplotlib, Ti\emph{k}Z/PGF, PSTricks, ggplot2, gnuplot, Graphviz.
\end{itemize}

\printbibliography[title=Publications]

\end{document}

%%% Local Variables:
%%% TeX-command-extra-options: "-shell-escape"
%%% TeX-engine: luatex
%%% TeX-master: t
%%% End:
